---
title       : Predicting Stock Prices with Change Point Detection
subtitle    : Using the CPM package
author      : Allen Hammock
job         : devdataprod-014
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The Premise

![The Author](https://avatars1.githubusercontent.com/u/543?v=3&s=230)

1. [Some have observed](http://www.researchgate.net/publication/224385407_A_Data_mining_algorithm_to_analyse_stock_market_data_using_lagged_correlation), we may be able to make short term
capital gains when two stocks traded on the market are strongly correlated together.

2. [One method](https://aschinchon.wordpress.com/2015/05/08/odd-connections-inside-the-nasdaq-100/) to
detect that two stocks appear to be **cointegrated** is to use the Augmented Dickey-Fuller test.

3. Perhaps we could explore various methods of [change point detection](http://things-about-r.tumblr.com/post/106806522699/change-point-detection-in-time-series-with-r-and)
with a Shiny app to see if significant changes in one stock might predict similar
changes in another stock?


--- 

## Detecting Change Points with CPM

```{r, eval = TRUE, fig.width = 13, fig.height = 3}
set.seed(8675309)
library(cpm)
df <- data.frame(t = seq(as.Date("2013-01-01"), as.Date("2013-01-01")+399, by="1 day"),
                 y = c(rnorm(200,0,1), rnorm(200,3,1)))
res <- detectChangePoint(df$y, cpmType = "Student", ARL0 = 500, startup = 20)
ggplot(df, aes(t, y)) + geom_line() +
  geom_vline(xintercept = as.numeric(df[res$detectionTime, c("t")]), col = 'blue') +
  geom_vline(xintercept = as.numeric(df[res$changePoint, c("t")]), col = 'red')
```

--- 

## Tracking Stock Market Changes with quantmod

```{r, eval = TRUE, fig.width = 13, fig.height = 3}
library(quantmod)
getSymbols("YHOO",src="google")
candleChart(YHOO,multi.col=TRUE,theme="white")
```

--- 

## Experiment with Change Point Detection on Shiny!

<!-- Limit image width and height -->
<style type='text/css'>
#slide-4 img {
    float: right;
    width: 50%;
    padding-left: 20px;
}
</style>

```{r fig.width=8, echo = FALSE}
library(png)
library(grid)
img <- readPNG("figures/shiny_app_fig_1.png")
grid.raster(img)
```
**Try it out yourself**
* [shinyapps.io](https://brainvat.shinyapps.io/DDPShinyPitch/)
* [github.com](https://github.com/brainvat/DDPShinyApp/tree/master)

**References**
* [Detecting change points in R and Tableau by Roberto Rösler][ref1]
* [Strange connections between stocks in NASDAQ by Antonio S. Chinchón][ref2]
* [Quantmod examples][ref3]

[ref1]: http://things-about-r.tumblr.com/post/106806522699/change-point-detection-in-time-series-with-r-and  "Change Point Detection in Time Series with R and Tableau"
[ref2]: https://aschinchon.wordpress.com/2015/05/08/odd-connections-inside-the-nasdaq-100/ "Odd Connections Inside The NASDAQ-100"
[ref3]: http://www.quantmod.com/examples/intro/ "Quantitative Financial Modelling & Trading Framework for R"
